%\underline{\textbf{Archived Journals in Print}}
\underline{\textbf{Archived Journals in Print (* denotes student)}}

\textbf{2019:}
\begin{enumerate}
  \item M.\ C.\ Recker*, E.\ J.\ Cazalas, J.\ W.\ McClory, and \textbf{J.\ E.\ Bevins}, ``Comparison of SiPM and PMT Performance Using a Cs2LiYCl6:Ce3+(CLYC) Scintillator with Two Optical Windows,” \textit{IEEE Transactions on Nuclear Science}, vol. 66, no. 8, pp. 1959–1965, 2019.

  \item Bethany L.\ Goldblum, Andrew W.\ Reddie, Thomas C.\ Hickey, \textbf{James E.\ Bevins}, et al., ``The nuclear network: Multiplex network analysis for interconnected systems," \textit{Applied Network Science}, vol. 4, no. 36, 2019.
  
   \item \textbf{J.\ E.\ Bevins}, Z.\ Sweger*, N.\ Munshi*, B.\ L.\ Goldblum, et al., ``Performance evaluation of an energy tuning assembly for neutron spectral shaping,” Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment, vol. 923, pp. 79–87, 2019.
\end{enumerate}

\textbf{2018:}
\begin{enumerate}
   \item R.\ Olesen*, B.\ E.\ O’Day, D.\ E.\ Holland, L.\ W.\ Burggraf, and \textbf{J.\ E.\ Bevins}, ``Characterization of Novel Rotating Scatter Mask Designs for Gamma Direction Identification," \textit{Nuclear Instrumentation and Methods in Physics Research Section A}, 2018. (In Press, available online)
      
  \item \textbf{James E.\ Bevins}, Elie Katzenson, James Kendrick, Rebecca Krentz-Wee, Sarah Laderman, Yubing Tian, ``A Framework for Assessing Alternate Proliferation Pathways in the Age of Non-State Actors,"  \textit{Nuclear Posture Review}, vol. 25, pp. 87-110, 2018. 
  
  \item M.\ K. Covo, R.\ A.\ Albright, B.\ F.\ Ninemire, M.\ B.\ Johnson, et al., ``The 88-Inch Cyclotron: A One-Stop Facility for Electronics Radiation and Detector Testing," \textit{Measurement}, vol 127, pp. 580-587, 2018. 
  
  \item D.\ E.\ Holland, \textbf{J.\ E.\ Bevins}, L.\ W.\ Burggraf, and B.\ E.\ O’Day, ``Rotating scatter mask optimization for gamma source direction identification,” \textit{Nuclear Instruments and Methods Phys. Res. A}, vol. 901, pp. 104–111, 2018.
  
  \item K.\ P.\ Harrig, B.\ L.\ Goldblum, J.\ A.\ Brown, D.\ L.\ Bleuel, L.\ A.\ Bernstein, \textbf{J.\ Bevins}, M.\ Harasty, T.\ A.\ Laplace, E.\ F.\ Matthews, ``Neutron Spectroscopy for Pulsed Beams with Frame Overlap using a Double Time-of-Flight Technique," \textit{Nuclear Instrumentation and Methods in Physics Research Section A}, vol. 877, pp. 359–366, 2018.

  \item \textbf{J.\ E.\ Bevins} and R.\ S.\ Slaybaugh, ``Gnowee: A Hybrid Metaheuristic Optimization Algorithm for Constrained, Black Box, Combinatorial Mixed-Integer Design,” \textit{Nuclear Technologies}, 2018.
\end{enumerate}

\textbf{2016:}
\begin{enumerate}
  \item N.\ Benczer-Koller, G.\ J.\ Kumbartzki, K.\ H.\ Speidel, D.\ A.\ Torres, et al., ``Magnetic moment and lifetime measurements of Coulomb-excited states in 106Cd," \textit{Physical Review C}, Vol. 94, 2016.
  
  \item G.\ J.\ Kumbartzki, N.\ Benczer-Koller, K.\ H.\ Speidel, D.\ A.\ Torres, et al., ``Z = 50 core stability in 110Sn from magnetic-moment and lifetime measurements," \textit{Physical Review C}, Vol. 93, 2016.
\end{enumerate}

% ------------------------------------------

\underline{\textbf{Limited Distribution Journal Articles, in Print }}
%\underline{\textbf{Limited Distribution Journal Articles, in Print (“*” denotes student)}}

\textbf{2012:}
\begin{enumerate}
  \item \textbf{J.\ Bevins}, K.\ Dahl, J.\ McClory, J.\ Petrosky, A.\ Caruso, and S.\ Karki, ``Bulk Radiation Damage Effects of a p-type B5C:Hx Thin Film on n-Si Heterojunction Diode," \textit{Journal of Radiation Effects, Research and Engineering}, Vol. 30, No1, 2012.
\end{enumerate}

% ------------------------------------------

\underline{\textbf{Refereed, In Process (* denotes student)}}

\begin{enumerate}
  \item Amy Hall*, Daniel A.\ Gum*, Richar Ferrieri, John Brockman, and \textbf{James E.\ Bevins}, ``Development of an Experimentally-Validated MCNP6 Model for $^{11}$C Production via the $^{14}$N(p,$\alpha$) Reaction Using a GE PETTrace Cyclotron,” \textit{Nuclear Technologies}, 2019. (Submitted August 2019)
  
  \item N.\ J.\ Quartemont*, R.\ Slaybaugh, and L.\ Bernstein, \textbf{J.\ E.\ Bevins}, ``Analysis of an Energy Tuning Assembly for Simulating Nuclear Weapon Environments at the National Ignition Facility,” \textit{Journal of Radiation Effects Research and Engineering}, 2019. (Submitted June 2019)

  \item B.\ V.\ Egner*, Darren Holland, Larry Burggraf, and \textbf{James E.\ Bevins}, ``Development of a Modular Mixed-Radiation Directional Rotating Scatter Mask Detection System,” \textit{Radiation Measurements}, 2019. (Submitted June 2019)

   \item W.\ D.\ Johnston*, M.\ L.\ Dexter, J.\ W.\ McClory, and \textbf{J.\ E.\ Bevins}, ``Simulating Surface-interacting nuclear Detonations using RECIPE and SHAMRC,” \textit{Journal of Radiation Effects Research and Engineering}, 2019. (Submitted June 2019)
  
  \item N.\ J.\ Quartemont*, A.\ A.\ Bickley, and \textbf{J.\ E.\ Bevins}, ``Nuclear Data Covariance Analysis in Radiation Transport Simulations Utilizing SCALE Sampler and the IRDFF Nuclear Data Library,” \textit{Transactions on Nuclear Science}, 2019. (Submitted March 2019)
  
\end{enumerate}

% ------------------------------------------

%\underline{\textbf{Publications in Conference Proceedings}}
\underline{\textbf{Publications in Conference Proceedings (* denotes student)}}

\begin{enumerate}
  \item Robert J.\ Olesen*, D.\ E.\ Holland, Erik Brubaker, James Cole, and \textbf{James E.\ Bevins}, ``Advanced Radiation Imaging Algorithms with Rotating Scatter Masks,” in \textit{International Nuclear Materials Management Conference}, Palm Desert, CA, July 18th, 2019.

  \item B.\ V.\ Egner*, D.\ E.\ Holland, L.\ W.\ Burggraf, \textbf{J.\ E.\ Bevins}, and V.\ M.\ Martin*, ``Development of a dual-particle directional detection system using a rotating scatter mask,” in \textit{Hardened Electronics and Radiation Technology Conference}, San Diego, CA, April 11th, 2019.

  \item W.\ D.\ Johnston*, M.\ L.\ Dexter, J.\ W.\ McClory, and \textbf{J.\ E.\ Bevins}, ``Validation of the Impact of Reflected Shock on Surface Interacting Nuclear Detonations,” in \textit{Hardened Electronics and Radiation Technology Conference}, San Diego, CA, April 10th, 2019.

  \item N.\ J.\ Quartemont*, \textbf{J.\ E.\ Bevins}, R.\ Slaybaugh, and L.\ Bernstein, ``Analysis of an Energy Tuning Assembly for Simulating Nuclear Weapon Environments at the National Ignition Facility,” in \textit{Hardened Electronics and Radiation Technology Conference}, San Diego, CA, April 11th, 2019.

  \item N.\ J.\ Quartemont*, \textbf{J.\ E.\ Bevins}, R.\ Slaybaugh, and L.\ Bernstein, ``Development of a Novel National Ignition Facility Platform for Simulating Nuclear Relevant Neutron Environments,” in \textit{IEEE Nuclear Science Symposium and Medical Imaging Conference}, Sydney, Australia, November 14th 2018.

  \item \textbf{J.\ E.\ Bevins}, S.\ Bogetic*, L.\ A.\ Bernstein, R.\ Slaybaugh, and J.\ Vujic, ``Metaheuristic Optimization Method for Neutron Spectra Shaping,” \textit{Transactions of the American Nuclear Society}, vol. 118, Philadelphia, PA, June 18th, 2018.
  
  \item D.\ E.\ Holland, \textbf{J.\ E.\ Bevins}, L.\ W.\ Burggraf, and B.\ E.\ O’Day, ``Rotating scatter mask optimization for gamma source direction identification,” presented at the \textit{Symposium on Radiation Measurement and Applications}, Ann Arbor, MI, June 14th, 2018.

  \item J.\ R.\ Stickney*, \textbf{J.\ E.\ Bevins}, E.\ Cazalas, and J.\ W.\ McClory, ``Pulse Height Spectra Analysis of a Neutron Energy Tuning Assembly,” presented at the \textit{Symposium on Radiation Measurement and Applications}, Ann Arbor, MI, June 13th, 2018.

  \item R.\ J.\ Olesen*, B.\ O.\ Day, D.\ Holland, L.\ Burggraf, and \textbf{J.\ Bevins}, ``Characterization of Rotating Scatter Mask Designs for Novel Applications in Photon Detection,” presented at the \textit{Symposium on Radiation Measurement and Applications}, Ann Arbor, MI, June 13th, 2018.

  \item Z.\ T.\ Condon*, L.\ W.\ Burggraf, J.\ V.\ Logan, B.\ E.\ O’Day, R.\ J.\ Olesen, \textbf{J.\ E.\ Bevins}, and J.\ C.\ Petrosky, ``Multisource Location Using a Rotating Scatter Mask to Predictably Attenuate Full Energy Gamma-Ray Emissions,” presented at the \textit{Hardened Electronics and Radiation Technology Technology Technical Interchange Meeting}, Tucson, AZ, April 19th, 2018.
  
  \item \textbf{James E.\ Bevins}, Bethany L.\ Goldblum, Elie Katzenson, James Kendrick, Rebecca Krentz-Wee, Sarah Laderman, Yubing Tian, ``Alternate Nuclear Proliferation Pathways in the Age of Non-State Actors," \textit{Transactions of the American Nuclear Society}, vol. 117, pp. 1009–1012, Washington, D.C., October 30th, 2017 (invited).
  
  \item M. K. Covo et al., ``88-Inch Cyclotron: The one-stop facility for electronics radiation testing," presented at \textit{IEEE International Workshop on Metrology for AeroSpace (MetroAeroSpace)}, pp. 484-488, Padua, July 2017.

  \item \textbf{James E.\ Bevins}, Bethany L.\ Goldblum, Tom Hickey, Elie Katzenson, James Kendrick, Rebecca Krentz-Wee, Sarah Laderman, Yubing Tian, Collin Ting, Alexa J Wehsener, ``Alternate Nuclear Proliferation Pathways in the Age of Non-State Actors," presented at \textit{Advances in Nuclear Nonproliferation Technology and Policy Conference}, Santa Fe, NM, September 2016.

  \item \textbf{J.\ Bevins}, R.\ Slaybaugh, L.\ Bernstein, E.\ Henry, W.\ Dunlop, ``Targeted Modification of Neutron Energy Spectra for National Security Applications," presented at \textit{Hardened Electronics And Radiation Technology Technical Interchange Meeting}, Monterey, CA, April 2016. 

  \item \textbf{J.\ Bevins}, R.\ Slaybaugh, L.\ Bernstein, W.\ Dunlop, E.\ Henry, ``Application of Metaheuristic Optimization Methods for Neutron Spectral Shaping Applications," presented at \textit{Conference on Data Analysis}, Santa Fe, NM, March 2016.
  
  \item G.\ Kumbartzki, N.\ Benczer-Koller, et al., ``Magnetic Moments of the 2$^+_1$ and 4$^+_1$ States in $^{110}$SN*,” presented at \textit{Fall Meeting of the APS Division of Nuclear Physics}, 2015, vol. 60, no. 13.
  
  \item A.\ Stevenson and \textbf{J.\ Bevins}, ``Project Nimble Elder: Investigation of Practical Solutions for Active Interrogation," presented at \textit{Hardened Electronics And Radiation Technology Technical Interchange Meeting}, Albuquerque, NM, April, 2013.
  
  \item A. Stevenson, J. St. Ledger, and \textbf{J. Bevins}, ``The AFNWC Nuclear Dust Cloud Modeling Initiative," presented at \textit{Hardened Electronics And Radiation Technology Technical Interchange Meeting}, Monterey, CA, March 2012.

  \item S.\ Karki, \textbf{J.\ E.\ Bevins}, Joseph Sandstrom, C.\ Clayton, M.\ S.\ Driver, B.\ Nordell, J.\ W.\ McClory, J.\ C.\ Petrosky , K.\ I.\ Pokhodnya and A.\ N.\ Caruso, ``Fabrication and transport properties of a-B5C:Hx to n-type Si heterojunction diodes", \textit{American Physical Society March Meeting}, Dallas, TX, March 2011. 
  
  \item Abigail A.\ Bickley, \textbf{James Bevins}, Anthony Caruso, James Petrosky, John McClory, Peter Dowben, and William Miller, `` Design and testing of a boron carbide based neutron spectrometer for homeland security applications," \textit{Abstracts Of Papers Of The American Chemical Society}, vol. 242. 1155, 2011.

  \item \textbf{James Bevins}, John McClory, James Petrosky, and Anthony Caruso, ``Theoretical Performance of a p-type B5C:Hx Thin Film on n-Si Neutron Detector", \textit{Transactions of the American Nuclear Society}, vol. 103, pp. 212-216, November 2010. 
  
  \item \textbf{J.\ Bevins}, J.\ P.\ Hayward, J.\ Mihalczo, ``Monte Carlo simulations of passive time correlation measurements for monitoring HEU in large storage arrays," \textit{Proceedings of 50th INMM Annual Meeting}, Tucson, AZ, July 2009.
\end{enumerate}
% ------------------------------------------

\underline{\textbf{Conference Presentations (not including publications listed above)}}

\begin{enumerate}
  \item P.\ Lalor*, Bethany L.\ Goldblum, Mathew Harasty, Joshua A.\ Brown, Thibault Laplace,  \textbf{James E.\ Bevins}, ``A Shape-constrained Neutron Spectrum Unfolding Technique,” presented at \textit{National Nuclear Security Administration University Program Review}, Raleigh, NC, June 5th, 2019.

  \item A.\ W.\ Burkhardt* and \textbf{J.\ E.\ Bevins}, ``Validation of Reactor Systems Transport Using KENO-VI Modeling,” presented at the \textit{American Nuclear Society Student Conference}, Richmond, VA, April 5th, 2019.

  \item D.\ A.\ Gum*, A.\ Hall, R.\ Ferrieri, J.\ Brockman, and \textbf{J.\ E.\ Bevins}, ``Characterizing a MURR GE PETrace Cyclotron Proton Beam Profile,” presented at the \textit{American Nuclear Society Student Conference}, Richmond, VA, April 5th, 2019.

  \item Z.\ Sweger*, \textbf{J.\ Bevins}, N.\ Munshi, B.\ Goldblum, D.\ Bleuel, and R.\ Slaybaugh, ``Foil Activation Analysis for Neutron Spectrum Unfolding,” presented at \textit{National Nuclear Security Administration University Program Review}, Ann Arbor, MI, June 7th, 2018.

  \item B.\ Egner*, R.\ Torzilli*, \textbf{J.\ E.\ Bevins}, and B.\ E.\ O’Day, ``Automated Parametric Optimization of a High-Purity Germanium Monte Carlo Neutral-Particle Model,” presented at the \textit{American Nuclear Society Student Conference}, Gainsville, FL, April 5th, 2018.

  \item T.\ A.\ Laplace, J.\ A.\ Brown, B.\ L.\ Goldblum, D.\ L.\ Bleuel, K.\ P.\ Harrig, \textbf{J.\ Bevins}, M.\ Harasty, ``Low Energy Light Yield of Organic Scintillators," University Program Review, 2017, Walnut Creek, CA.
  
  \item \textbf{J.\ Bevins}, ``Modification of the NIF Neutron Spectrum for Forensics Applications," University and Industry Technical Interchange Review Meeting, 2016, Raleigh, NC.
  
  \item \textbf{James E.\ Bevins}, Bethany L.\ Goldblum, Tom Hickey, Elie Katzenson, James Kendrick, Rebecca Krentz-Wee, Sarah Laderman, Yubing Tian, Collin Ting, Alexa J Wehsener, ``Alternate Nuclear Proliferation Pathways in the Age of Non-State Actors," University and Industry Technical Interchange Review Meeting, 2016, Raleigh, NC.

  \item \textbf{James Bevins}, Elie Katzenson, Tom Hickey, Erika Suzuki, James Kendrick, Nils Haneklaus, Yubing Tian, Bethany L. Goldblum, ``Rethinking the Proliferation Paradigm: Alternate Nuclear Weapon Paths in the Age of Non-State Actors and Technology Democratization," 2015 Winter Project on Nuclear Issues Conference, Washington DC, 2015.
  
  \item \textbf{J.\ Bevins}, ``NIF Fission-Enhanced Tailored-Spectrum Irradiator," Sather Workshop, 2014, Berkeley, CA.
  
  \item \textbf{J.\ Bevins}, B.\ Kowash, and J.\ McClory, ``Calibration of AFIT Graphite Pile to Account for 241Am Ingrowth in the 239PuBe13 Source," ANS National Student Conference, 2010, Ann Arbor, MI.
\end{enumerate}

% ------------------------------------------

\underline{\textbf{Other Works}}

\begin{enumerate}

\item Holland, D., Olesen, R.*, Burggraf, L., O’Day, B., \textbf{Bevins, J}.  2019. ``Rotating Scatter Mask Design Classes for Directional Radiation Detection and Imaging.” U.S. Patent Application 62,816,435, filed March 11, 2019. Patent Pending.

\item Olesen, R.*, Egner, B.*, Holland, D., Martin, V.*, \textbf{Bevins, J}. 2019. ``An Efficient, Dual-particle Directional Detection System using a Rotating Scatter Mask.” U.S. Patent Application 62,816,451, filed March 11, 2019. Patent Pending.

\item \textbf{J.\ E.\ Bevins}, R.\ S.\ Slaybaugh, ``Energy Tuning Assembly for Post-Detonation Nuclear Forensics,” Invention Discolure, January, 2018.

\item \textbf{James Bevins}, Youdong Zhang, and Rachel Slaybaugh. ``Coeus." Software. (released 2017) \url{https://github.com/SlaybaughLab/Coeus} 

\item \textbf{James Bevins}, Youdong Zhang, and Rachel Slaybaugh. ``Gnowee." Software. (released 2017) \url{https://github.com/SlaybaughLab/Gnowee}
\end{enumerate} 
