\begin{bibsection}
  
  \item M.\ C.\ Recker*, E.\ J.\ Cazalas, J.\ W.\ McClory, and \textbf{J.\ E.\ Bevins}, ``Comparison of SiPM and PMT Performance Using a Cs2LiYCl6:Ce3+(CLYC) Scintillator with Two Optical Windows,” \textit{IEEE Transactions on Nuclear Science}, vol. 66, no. 8, pp. 1959–1965, 2019.

  \item Bethany L.\ Goldblum, Andrew W.\ Reddie, Thomas C.\ Hickey, \textbf{James E.\ Bevins}, et al., ``The nuclear network: Multiplex network analysis for interconnected systems," \textit{Applied Network Science}, vol. 4, no. 36, 2019.
  
   \item \textbf{J.\ E.\ Bevins}, Z.\ Sweger*, N.\ Munshi*, et al., ``Performance evaluation of an energy tuning assembly for neutron spectral shaping,” Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment, vol. 923, pp. 79–87, 2019.

   \item R.\ Olesen*, B.\ E.\ O’Day, D.\ E.\ Holland, L.\ W.\ Burggraf, and \textbf{J.\ E.\ Bevins}, ``Characterization of Novel Rotating Scatter Mask Designs for Gamma Direction Identification," \textit{Nuclear Instrumentation and Methods in Physics Research Section A}, 2018. (In Press, available online)
      
  \item \textbf{James E.\ Bevins}, Elie Katzenson, et al., ``A Framework for Assessing Alternate Proliferation Pathways in the Age of Non-State Actors,"  \textit{Nuclear Posture Review}, vol. 25, pp. 87-110, 2018. 
  
%  \item M.\ K. Covo, R.\ A.\ Albright, B.\ F.\ Ninemire, M.\ B.\ Johnson, et al., ``The 88-Inch Cyclotron: A One-Stop Facility for Electronics Radiation and Detector Testing," \textit{Measurement}, vol 127, pp. 580-587, 2018. 
  
  \item D.\ E.\ Holland, \textbf{J.\ E.\ Bevins}, et al., ``Rotating scatter mask optimization for gamma source direction identification,” \textit{Nuclear Instruments and Methods Phys. Res. A}, vol. 901, pp. 104–111, 2018.
  
  \item K.\ P.\ Harrig, B.\ L.\ Goldblum, et al., ``Neutron Spectroscopy for Pulsed Beams with Frame Overlap using a Double Time-of-Flight Technique," \textit{Nuclear Instrumentation and Methods in Physics Research Section A}, vol. 877, pp. 359–366, 2018.

  \item \textbf{J.\ E.\ Bevins} and R.\ S.\ Slaybaugh, ``Gnowee: A Hybrid Metaheuristic Optimization Algorithm for Constrained, Black Box, Combinatorial Mixed-Integer Design,” \textit{Nuclear Technologies}, 2018.
  
\item \textbf{James E.\ Bevins}, Rebecca Krentz-Wee, et. al., ``Alternate Nuclear Proliferation Pathways in the Age of Non-State Actors," in Proceedings of the American Nuclear Society Winter Meeting and Technology Expo, Washington, D.C., October 2017. (invited)

  \item N.\ Benczer-Koller, G.\ J.\ Kumbartzki, et al., ``Magnetic moment and lifetime measurements of Coulomb-excited states in 106Cd," \textit{Physical Review C}, Vol. 94, 2016.

  \item G.\ J.\ Kumbartzki, N.\ Benczer-Koller, et al., ``Z = 50 core stability in 110Sn from magnetic-moment and lifetime measurements," \textit{Physical Review C}, Vol. 93, 2016.

\item \textbf{J.\ Bevins}, K.\ Dahl, et al., ``Bulk Radiation Damage Effects of a p-type B5C:Hx Thin Film on n-Si Heterojunction Diode," \textit{Journal of Radiation Effects, Research and Engineering}, Vol. 30, No1, 2012.
  
\end{bibsection}

